Data Processing

### 2019-11-08 analysis/data_processing.Rmd
add second simulation
fix minor bugs before start testing

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)

@@

@@

>>>>

library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)

@@

data <- raw_data %>%
  filter(trial != "training", 
         trial != "filler1", 
         trial != "filler2",
         trial != "train",
         trial != "train2")%>%
  filter(phase == "shape" | is.na(phase))%>%
  select(subid, subage, test_date, task, trial, correct)%>%
  mutate(subid = str_replace(subid,"-","_"))%>%
  separate(subid, into = c("id","test_day"), sep="_")

raw_data %>%
  filter(
         trial == "filler1" | 
         trial == "filler2")

@@

```{r}
data%>%
  group_by(task)%>%
  summarise(n= length(unique(id)))
```

```{r}
p1 <- data%>%
  group_by(id,subage,task)%>%
  summarise(mean = mean(correct))

p2 <- p1 %>%
  group_by(subage,task)%>%
  multi_boot_standard(col = "mean")

ggplot()+
  geom_hline(yintercept = .5, lty = 2)+
  geom_line(data = p2,aes(x = subage, y = mean, group = task), alpha = .5)+
  geom_jitter(data = p1, aes(x = subage, y = mean, col = subage), alpha = .5, width = .2, height = .01)+
  geom_pointrange(data = p2, aes(x = subage, y = mean, ymin = ci_lower, ymax = ci_upper, col = subage))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol()+
  theme_few()
